---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# utilitybeltrefseq

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)

<!-- badges: end -->

The goal of utilitybeltrefseq is to make it easy to find and download the best refseq assemblies available for any given species. All you need to know is the species [NCBI taxonomy ID](https://www.ncbi.nlm.nih.gov/taxonomy)

## Installation

You can install the development version of utilitybeltrefseq from [GitHub](https://github.com/selkamand/utilitybeltrefseq) with:

``` r
# install.packages("devtools")
devtools::install_github("selkamand/utilitybeltrefseq")
```

## Example

Say you want to find the best reference genome for *Escherichia coli*.

First we download a list of available assemblies from refseq.

```{r echo=TRUE, eval=FALSE}
library(utilitybeltrefseq)
load_refseq_data_frame_from_ftp()
```

For best results, run the above command every couple of months to stay up to date with whats currently in refseq.

Next, we need to find the NCBI taxonomy ID of our species of interest. We can find that [here](https://www.ncbi.nlm.nih.gov/taxonomy) (taxid: 562). We could also have used the **taxize** package if we wanted to stay within R.

Now that we have the species level taxid, we can run `choose_best_assembly`

```{r}
choose_best_assembly(taxid_of_interest = 562)
```

Note that we get a warning that there are multiple 'best' assemblies. If there are multiple strains in a species with complete assemblies - it his hard to know which to return. We choose the most recently added assembly. To return all of the high quality assemblies you can run:

```{r}
 choose_best_assembly(
   taxid_of_interest = 562, 
   break_ties_based_on_newest_sequence_added = FALSE,
   return_accession_only = TRUE # set this to false to get more info about each assembly
   )
```

Keep an eye on the intraspecific name column. Often can use this to choose which strain you're after. See `?choose_best_assembly` for details.

Once we have the assembly accession we're interested in, we can download it:

```{r, eval=FALSE}
 download_assembly(
   target_assembly_accession = GCF_000005845.2
   )
```

If we just want to quickly download a ref-genome of our species of interest we can just run

```{r, eval=FALSE}
download_best_assembly(taxid_of_interest = 562)
```
